Solving a probabilistic planning problem by presenting a history in the field of probabilistic planning

### 2014-04-13 FinalPaper/paper.tex
Add prob interstingness of domain to conclusion

As the current planning domain is probabilistically interesting, the
\textsc{Gourmand} planner is favorable. However, by modifying the drone's
communication protocol by adding a handshake protocol any communication failure
can be detected. The UAV can therefore choose to initiate another transmission
of the message until it received an acknowledgment. This way the dead-ends are
replaced with higher costs actions similarly to the \textsc{Navigation} domain.
These higher cost actions are however somewhat more realistic as they do not
mean the disappearance of a highly expensive piece of equipment, but rather a
data package. As this is a realistic and often occurring communicating
protocol, we believe that FF-Replan is in fact a proper alternative for the
current state-of-the-art probabilistic planner.

>>>>

In the domain several goal paths follow the state-action sequences. However,
the UAVs can decide to send a package to a closer neighbor rather than a
further one. This increases the amount of time necessary, but decreases the
probability of the package not being received. This means the domain is
probabilistically interesting.

As the current planning domain is probabilistically interesting, the
\textsc{Gourmand} planner is favorable. However, by modifying the drone's
communication protocol by adding a handshake protocol any communication failure
can be detected. The UAV can therefore choose to initiate another transmission
of the message until it received an acknowledgment. This way the dead ends are
replaced with higher costs actions similarly to the \textsc{Navigation} domain.
These higher cost actions are however somewhat more realistic as they do not
mean the disappearance of a highly expensive piece of equipment, but rather a
data package. As this is a realistic and often occurring communicating
protocol, we believe that FF-Replan is in fact a proper alternative for the
current state-of-the-art probabilistic planner.
